Extended Data

### 2021-11-16 doc/manuscript/Dow_manuscript_Nature.Rmd
Update Dow_manuscript_Nature.Rmd

Here, we evaluate how early spring temperatures affect stem growth phenology, growth rates, and annual growth of temperate deciduous trees across eastern North America. 
To test whether warmer springs extend the period of stem growth, we used dendrometer band measurements on `r n_dendro_trees` trees across two mid-latitude forests. 
To test whether spring temperatures consistently increased annual growth, we used `r n_chronologies` tree-ring chronologies from `r n_cores_sites` forests.

>>>>

Here, we evaluate how early spring temperatures affect stem growth phenology, growth rates, and annual growth of temperate deciduous trees across eastern North America. 
To test whether warmer springs extend the period of stem growth, we used dendrometer band measurements on `r n_dendro_trees` trees across two mid-latitude forests. 
To test whether spring temperatures consistently increased annual growth, we analyzed `r n_chronologies` tree-ring chronologies from `r n_cores_sites` forests.
